\documentclass[letterpaper, 12pt]{article}

\title{Constructors}
\author{Amiel L. Iliesi}
\date{2026-03-27}

% packages
\usepackage[hidelinks]{hyperref}

% commands
\newcommand{\question}[2][4em]{\textbf{#2}\vspace{#1}\par}

% global options
\setlength{\parindent}{0pt}

\begin{document}

\maketitle

\tableofcontents

\pagebreak
\section{Dynamic Memory}

\subsection{Dynamic Element}
\question{How do you initialize a single element of type \texttt{T}?}
\question{How do you deallocate that same element?}
\question{When do you deallocate that element?}

\subsection{Dynamic Array}
\question{How do you initialize an array of length \texttt{N}, of type
\texttt{T}?}

\question{How do you deallocate that array?}

\pagebreak
\section{Constructors}

\subsection{Rule of Three}
\question{Describe the rule of three}

\question{\textit{[extra credit]:} Describe the rule of five, and the rule of
zero, if you know them.}

\subsection{Default Constructor}
\question{What is the default construtor?}

\question{What are the two ways a default constructor can become unavailable?}

\question{How can you ask the program that default constructor be
re-established?}

\subsection{Copy Constructor}
\question{What is a copy constructor?}

\question{Given that you have a type \texttt{T}, with a dynamic member
\texttt{int x}, write a copy constructor for \texttt{T}.}

\subsection{Copy Assignment Operator}
\question{Given a type \texttt{T}, write the prototype for its copy assignment
operator.}

\question{What is the difference between a copy constructor, and a copy
assignment operator?}

\subsection{Parameterized Constructors}
\question{What is a parameterized constructor?}

\question{If I had a type \texttt{T} with members \texttt{char c}, and
\texttt{int x}, how would you make a parameterized constructor that sets all of
\texttt{T}'s members?}

\pagebreak
\section{Destructors}
\question{What is a destructor? What is its purpose?}

\question{When do you need a destructor?}

\question{How do you invoke a destructor?}

\end{document}