\documentclass[12pt, letterpaper]{article}

\title{CS302: Testing}
\author{Amiel L. Iliesi}
\date{2026-04-08}

% packages
\usepackage[hidelinks]{hyperref}
\usepackage[x11names]{xcolor}

% new commands
\newcommand{\question}[2][4em]{\textbf{#2}\vspace{#1}\par}
\newcommand{\answer}[1]{\color{Green4}\textbf{#1}\normalcolor}

% new environments
\newenvironment{answerblock}{\color{Green4}}{\normalcolor\vspace{1em}}

% global settings
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\begin{document}

\maketitle

\tableofcontents

\pagebreak
\section{Testing Data Structures}

\question[8em]{In the following sections we will outline a few ways to test data
structures. What do the tests tell us about our data structure, if they all
pass?}

\question[8em]{What might happen if we forgo testing our data structures? What
benefits does testing give to us programmers \emph{while} we are building the
data structure?}

\pagebreak
\section{Blackbox}

\question[12em]{Describe blackbox testing. What does it test, what is known while
testing?}

\question[12em]{If you wanted to blackbox test a balanced binary tree, what are some
tests you could implement?}

\pagebreak
\section{Glassbox}

\question[12em]{Describe glassbox testing. What does it test, what is known while
testing?}

\question[12em]{If you wanted to glassbox test a balanced binary tree, what are some
tests you could implement?}

\pagebreak
\section{Unit Testing}

\question[8em]{What is the point of unit testing? Describe an environment where you
would see this, and the purpose it fulfills.}

\question[20em]{Write a basic unit test, and show it's execution. Do this
however you like, C++, Python, pseudocode, just be specific.}

\question{BONUS: do you know the other big two types of software testing?}

\end{document}