\documentclass[12pt, letterpaper]{article}

\title{Recursion}
\author{Amiel L. Iliesi}
\date{2026-03-27}

% packages
\usepackage[hidelinks]{hyperref}
\usepackage[x11names]{xcolor}
\usepackage{minted}

% new commands
\newcommand{\question}[2][4em]{\textbf{#2}\vspace{#1}\par}
\newcommand{\answer}[1]{\color{Green4}\textbf{#1}\normalcolor}

% new environments
\newenvironment{answerblock}{\color{Green4}}{\normalcolor}

% global settings
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}
\usemintedstyle{monokai}

\begin{document}

\maketitle

\tableofcontents

\pagebreak
\section{Terminology}

\question{What are base cases?}

\question{What are recursive cases?}

\question{What is recursive depth? Stack depth?}

\question[12em]{Describe the differences between preorder, in-order, and postorder
traversal. Also, which are synonyms with head recursion, and tail recursion?}

\question{When possible, why is \emph{tail recursion} preferable?}

\pagebreak
\section{Conversion From Iteration to Recrusion}

\question[0em]{Convert the following into a recursive function.}

\begin{minted}[style=bw]{cpp}
int sum = 0;
for (int i = 1; i < N; ++i) {
    sum += i;
}
\end{minted}
\vspace{14em}

\question{What parts can you systematically translate? Identify the
relationship these pieces dictate between recursion and iteration.}

\pagebreak
\section{Uniquely Recursive}

\question{Describe the relationship between recursion and iteration.}

\question{To expand on the previous question, what can recursion do that
iteration cannot?--and vice versa.}

\question{Why is iteration preferable when possible?}

\question{What situations can have a iterative \textit{and} recursive solution,
but have the recursive solution be preferable?}

\end{document}